Trends of SDR in Thessaloniki

### 2023-10-10 Article.Rmd
Commit 2023-10-10 09:14

Although the trends suggest that raw data have a homogeneous behavior, using plots of the cumulative sum (CUSUM) of the computed anomalies, we can reveal some structure within the trends and some differences between the sky conditions [@Regier2019]. 
On all three plots on Figure\ \ref{fig:cusum}, we observe a downward part at the start of the period until about 2000, an almost steady part until about 2016 for all-sky and clear-sky conditions (Figures\ \ref{fig:cusum-1}, \ref{fig:cusum-2}) and until 2009 for cloud-sky conditions (Figure\ \ref{fig:cusum-3}), and finally, a steep upward part until the present.
For a uniform trend, we would expect the cumulative sums of the anomalies to have a symmetric 'V' shape.
This would indicate that the anomalies are evenly distributed around the climatological mean.
In our case, for all sky conditions, we observe periods where the CUSUMs remain relative steady, roughly around the middle of the study dataset.
Another distinct feature of the CUSUMs, is the different pattern of the cloudy-sky dataset which peaks around the middle of the period.
The CUSUMs of the clear and the all-sky conditions exhibit similar patterns.
The causes for these discrepancies haven't been investigated yet.

@@

<!-- ```{r echo = FALSE, fig.cap='SDR trend ~ SZA', fig.subcap=c('', '', ''), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-1.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-2.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-3.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-4.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-5.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-6.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-7.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-8.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-9.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-10.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-11.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsSeas-12.png") -->
<!-- ``` -->

>>>>

Although the year-to-year variability of the anomalies in Figure \ref{fig:trendALL} shows a rather homogeneous behavior, plots of the cumulative sums (CUSUM) of the anomalies can reveal structures which are different for the three sky conditions [@Regier2019]. 
On all three plots on Figure\ \ref{fig:cusum}, we observe a downward part at the start of the period until about 2000, an almost steady part until about 2016 for all-sky and clear-sky conditions (Figures\ \ref{fig:cusum-1}, \ref{fig:cusum-2}) and until 2009 for cloud-sky conditions (Figure\ \ref{fig:cusum-3}), and finally, a steep upward part until the present.
For a uniform trend, we would expect the cumulative sums of the anomalies to have a symmetric 'V' shape.
This would indicate that the anomalies are evenly distributed around the climatological mean.
In our case, for all sky conditions, we observe periods where the CUSUMs remain relative steady, roughly around the middle of the study dataset.
Another distinct feature of the CUSUMs, is the different pattern of the cloudy-sky dataset which peaks around the middle of the period.
The CUSUMs of the clear and the all-sky conditions exhibit similar patterns.
The causes for these discrepancies haven't been investigated yet.

@@
